Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-05-25 tacl.tex
fixed numbers

				Lattice & \bf{0.67} & 0.44 & \bf{0.54} & & \bf{0.40}& \bf{0.60} & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
            \bottomrule

 \end{tabular}
  \caption{ Results of FS identification in various test sets; Countrank= lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score. Bold is best in column. For the ICWSM only, difference relative to best baseline is significant at the $ p < 0.5$ level; the difference for all test sets considered together is significant at the $ p < 0.01$ level}
	 \label{tab:main}

@@

       \toprule
			& P & R & F\\
			 \midrule
			PMIrank & 0.20 & 0.29 & 0.23 \\
			minLPRrank & 0.34 & 0.45 & 0.39 \\
			LPR-seg & 0.42 & 0.45 & 0.43 \\
			LocalMaxs & \bf{0.56} & 0.39 & 0.46 \\
			DP-seg & 0.35 & \bf{0.71} & 0.47 \\
  \midrule
			Lattice & 0.47 & 0.63 & \bf{0.54} \\
       \bottomrule
 \end{tabular}
  \caption{ Results of FS identification in contiguous BNC test set; LocalMaxs = method of da Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
	\label{tab:BNC}

>>>>

				Lattice & \bf{0.67} & 0.44 & \bf{0.54} & & \bf{0.38}& 0.58 & \bf{0.46} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
            \bottomrule

 \end{tabular}
  \caption{ Results of FS identification in various test sets; Countrank= lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score. Bold is best in column. For the ICWSM only, f-score difference relative to best baseline is significant at the $p < 0.5$ level; the difference for all test sets together is significant at the $ p < 0.01$ level}
	 \label{tab:main}

@@

       \toprule
			& P & R & F\\
			 \midrule
			PMIrank & 0.20 & 0.29 & 0.23 \\
			minLPRrank & 0.34 & 0.45 & 0.39 \\
			LPR-seg & 0.42 & 0.45 & 0.43 \\
			LocalMaxs & \bf{0.56} & 0.39 & 0.46 \\
			DP-seg & 0.35 & \bf{0.71} & 0.47 \\
  \midrule
			Lattice & 0.46 & 0.61 & \bf{0.53} \\
       \bottomrule
 \end{tabular}
  \caption{ Results of FS identification in contiguous BNC test set; LocalMaxs = method of da Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
	\label{tab:BNC}
